\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
	\usepackage[T1]{fontenc}
	\usepackage[utf8]{inputenc}
\else % if luatex or xelatex
	\ifxetex
	\usepackage{mathspec}
\else
	\usepackage{fontspec}
\fi
\defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
	\usepackage{microtype}
	\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
	}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
	pdfborder={0 0 0},
	breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
	\usepackage{parskip}
	}{% else
	\setlength{\parindent}{0pt}
	\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
	\let\oldparagraph\paragraph
	\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
	\let\oldsubparagraph\subparagraph
	\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

\section{BIOL 01.24.17}\label{biol-01.24.17}

\subsection{2nd, 3rd, 4th structures}\label{nd-3rd-4th-structures}

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\tightlist
	\item
	      Ionic: stong.
	\item
	      Hydrogren bonding: hydration shell.

	      \begin{itemize}
	      	\tightlist
	      	\item
	      	      responsible for 2ndary structures.
	      \end{itemize}
	\item
	      Van der Vaals: weak
	\item
	      Hydrophobic interactions: \textbf{NOT BONDS}, reducing needs for
	      highly ordered water molecules.

	      \begin{itemize}
	      	\tightlist
	      	\item
	      	      Bond strength:

	      	      \begin{enumerate}
	      	      	\def\labelenumii{\arabic{enumii}.}
	      	      	\tightlist
	      	      	\item
	      	      	      Van
	      	      	\item
	      	      	      Ionic
	      	      	\item
	      	      	      Hbond
	      	      	\item
	      	      	      C-C
	      	      	\item
	      	      	      C=C
	      	      \end{enumerate}
	      \end{itemize}
\end{enumerate}

\subsection{2ndary structure's rules}\label{ndary-structures-rules}

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\tightlist
	\item
	      Xray diffraction: interatomic bond distances, angles of amino acids
	      chains.
	\item
	      Theoreticral analysis of angles
	\item
	      \textbf{Something else here yo.}

	      \begin{itemize}
	      	\tightlist
	      	\item
	      	      Planar rotation limitations

	      	      \begin{enumerate}
	      	      	\def\labelenumii{\arabic{enumii}.}
	      	      	\tightlist
	      	      	\item
	      	      	      \phi
	      	      	\item
	      	      	      \psi
	      	      \end{enumerate}
	      \end{itemize}
	\item
	      Alpha-helix with \textbf{3.6} amino acids/turn

	      \begin{itemize}
	      	\tightlist
	      	\item
	      	      Rise from one alphacarbon-alphacarbond is 1.5 angstrom
	      \end{itemize}
\end{enumerate}

\subsection{Jan 26, 2017}\label{jan-26-2017}

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\setcounter{enumi}{4}
	\tightlist
	\item
	      Pitch is 5.4 Angstrom
	\item
	      Linus' mistake

	      \begin{itemize}
	      	\tightlist
	      	\item
	      	      L steriomer
	      	\item
	      	      Rght handed helix
	      \end{itemize}
	\item
	      Helix or not?

	      \begin{enumerate}
	      	\def\labelenumii{\arabic{enumii}.}
	      	\tightlist
	      	\item
	      	      Similarly charged residues disrupts helixformation.
	      	\item
	      	      If too many large aminoacids consecutively, helix disrupted.
	      	\item
	      	      Bonding between R groups 3---4 residues apart stabilize.
	      	\item
	      	      P destabilizes helix; \textbf{Proline destabilizes}.
	      	\item
	      	      Negative N terminus, positive C terminus stabilizes helix.

	      	      \begin{itemize}
	      	      	\tightlist
	      	      	\item
	      	      	      Leads to dipole across peptide bond.
	      	      \end{itemize}
	      \end{enumerate}
	\item
	      Circular dichroism

	      \begin{itemize}
	      	\tightlist
	      	\item
	      	      Random coil, betasheet, alphahelix interact with light differently.
	      	\item
	      	      Measures amount of secondary structures.
	      \end{itemize}
	\item
	      Betasheet

	      \begin{itemize}
	      	\tightlist
	      	\item
	      	      3.5 angstrom between adjacent amino acids, vs.~1.5 in alphahelix.
	      	\item
	      	      Fully extended.
	      	\item
	      	      Antiparallel arrangemet of adjacent betastrands.
	      	\item
	      	      Adjacent polypeptide strands an be parallel or antiparallel.
	      \end{itemize}
	\item
	      Folding

	      \begin{itemize}
	      	\tightlist
	      	\item
	      	      Fewer than 1/billion random polypeptides folds into organized
	      	      structures.
	      	\item
	      	      Folding energy is low; most protein close to unfolded state.
	      	\item
	      	      Genes encoded for folding seleted by evolution.
	      	\item
	      	      Folded diffently every time.
	      \end{itemize}
\end{enumerate}

\end{document}
